---
title: "R Notebook"
output:
  pdf_document: default
  html_notebook: default
---

```{r}
library(knitr)
library(tidyverse)
library(cowplot)
theme_set(theme_cowplot())
```

```{r}
landings_raw <- readODS::read_ods('landing_data_reformatted.ods', 
                              sheet=1, 
                              col_names = TRUE)
```


```{r}
landings_raw %>%
  separate(measure, c("coordinate", "alt", "other"), sep='[()]') %>%
  extract(condition, c("experiment", "update_rate", "wind"), "(\\d). (.*?) (.*)") %>%
  select(-other) %>%
  mutate(alt = fct_relevel(alt, "alt 0-5", "alt 5-10", "alt 10-20", "alt 20+")) %>%
  mutate(update_rate = fct_relevel(update_rate, "nfold_10fps", "nfold_2fps", "nfold_1fps", "nfold_0.5fps")) %>%
  mutate(wind = fct_recode(wind, 
                           "0 m/s" = "nowind", 
                           "8 m/s" = "wind 8m/s", 
                           "12 m/s" = "wind 12m/s")) %>%
  mutate(wind = fct_relevel(wind, "0 m/s", "8 m/s", "12 m/s")) %>%
  mutate(update_rate = fct_recode(update_rate, 
                                  "10" = "nfold_10fps", 
                                  "2" = "nfold_2fps", 
                                  "1" = "nfold_1fps", 
                                  "0.5" = "nfold_0.5fps")) %>%
  mutate(coordinate = str_replace(coordinate, "mse_", "")) %>%
  mutate(alt = fct_recode(alt, 
                          "0m - 5m" = "alt 0-5", 
                          "5m - 10m" = "alt 5-10", 
                          "10m - 20m" = "alt 10-20", 
                          "20m - " = "alt 20+")) ->
  landings_formatted
```
```{r}
landings_formatted %>%
  head()
```



```{r QoSLanding, fig.width=6, fig.height=4}
landings_formatted %>%
  ggplot() + 
  aes(x = measured_value, 
      y = update_rate, 
      shape=coordinate, 
      color=wind) + 
  geom_point() + 
  facet_wrap(~alt) + 
  #scale_color_manual(values = c("grey", "black")) + 
  labs(x = 'Mean squared error [meter^2]', 
       y = 'Update rate [fps]', 
       color = 'Wind', 
       shape = 'Coordinate') + 
  theme_cowplot(font_size = 8) + 
  theme() -> p
p
ggsave('QoSLanding.pdf', p, width = 8, height=4.5, unit="cm")
```


```{r}
landing_precision_raw <- readODS::read_ods('landing_precision_reformatted.ods', sheet = 1)
```

```{r}
landing_precision_raw %>%
  extract(condition, c("experiment", "update_rate", "wind"), "(\\d). (.*?) (.*)") %>%
  mutate(wind = fct_recode(wind, 
                           "0" = "nowind", 
                           "8" = "wind 8m/s", 
                           "12" = "wind 12m/s")) %>%
  mutate(update_rate = fct_recode(update_rate, 
                           "0.5" = "nfold_0.5fps", 
                           "1" = "nfold_1fps", 
                           "2" = "nfold_2fps", 
                           "10" = "nfold_10fps")) ->
  landing_precision
```


```{r}
landing_precision %>%
  ggplot() + 
  aes(x = accuracy_x, 
      y = wind) + 
  geom_point()
```




```{r}
object_detection_raw <- readODS::read_ods('object_detection_reformatted.ods', 
                                          col_names = TRUE,
                                          col_types = cols(
                                            condition = col_character(),
                                            object_number = col_double(),
                                            object_class = col_double(),
                                            detected = col_character(),
                                            correct = col_character(),
                                            mse_x = col_double(),
                                            mse_y = col_double()
                                          ))
```

```{r}
head(object_detection_raw)
```



```{r}
object_detection_raw %>%
  extract(condition, 
          c("experiment", "yolo_fps", "nfold_fps", "wind"), 
          "(\\d). \\(Yolo_(.*)fps\\) \\(nfold_(.*)fps\\) \\((.*)\\)") %>%
  mutate(wind = fct_recode(wind, 
                           "0" = "NoWindSpeed", 
                           "8" = "WindSpeed_8m/s", 
                           "8" = "WindSpeed 8m/s", 
                           "12" = "WindSpeed 12m/s", 
                           "12" = "WindSpeed 12 m/s", 
                           "12" = "WindSpeed_12m/s")) %>%
  mutate(wind = fct_relevel(wind, "0", "8", "12")) %>%
  mutate(yolo_fps = factor(as.numeric(yolo_fps))) %>%
  mutate(nfold_fps = factor(as.numeric(nfold_fps))) %>%
  mutate(object_number = factor(object_number)) %>%
  mutate(object_class = factor(object_class)) %>%
  mutate(detected = factor(detected)) %>%
  mutate(correct = correct == 'yes') ->
  object_detection
```

```{r}
object_detection %>%
  ggplot() + 
  aes(x = mse_x, 
      y = mse_y) + 
  geom_point(aes(color = wind)) + 
  facet_grid(yolo_fps ~ nfold_fps) + 
  labs(x = "Mean Squared Error x (meter)",
       y = "Mean Squared Error y (meter)", 
       title = "Error in x and y directions", 
       subtitle = "Faceted on yolo fps (0.1 and 4) and nfold fps (0.5 and 10)")
```

I see not direction relation between the errors in x and y directions 
in this plot.





```{r}
object_detection %>%
  group_by(experiment, wind, yolo_fps, nfold_fps) %>%
  summarise(correct = sum(correct), 
            .groups = "drop_last") %>%
  arrange(desc(correct))
```

```{r}
object_detection %>%
  group_by(experiment, wind, yolo_fps, nfold_fps) %>%
  summarise(correct = sum(correct), 
            .groups = "drop_last") %>%
  filter(wind == 8)
```


```{r QoSDetection}
object_detection %>%
  group_by(experiment, wind, yolo_fps, nfold_fps) %>%
  summarise(correct = sum(correct), 
            .groups = "drop_last") %>%
  ggplot() +
  aes(x = correct, 
      y = wind, 
      color = sprintf("%s fps", yolo_fps), 
      shape = sprintf("%s fps", nfold_fps)) + 
  geom_jitter(height = 0, width=0.2) + 
  scale_color_manual(values = c("0.1 fps" = "grey", 
                                "4 fps" = "black")) + 
  scale_x_continuous(limits = c(15, 32)) +
  labs(color = "YOLOv3 tiny", 
       shape = "n-fold",
       y = "Wind [m/s]", 
       x = "Number of correct detections (max 32)") +
  theme_cowplot(font_size = 8) +
  theme(legend.position = c(1.0, 1.0), 
        legend.justification=c(1,1), 
        legend.box = "horizontal", 
        legend.box.background = element_rect(color='black', size=0.2), 
        legend.box.margin = margin(0.1, 0.1, 0.1, 0.1, 'cm')) +
  guides(color = guide_legend(order = 1), 
         shape = guide_legend(order = 2)) -> p
p
ggsave('QoSDetection.pdf', p, width = 8, height=4.5, unit="cm")
```

Observations: 
1. The number of correct detections increase when the wind is reduced.
2. The number of correct detections increase when the yolo frame rate is increased.
3. There are no clear relation with the nfold edge frame rate.


# Plotting power consumption during landing

```{r}
power_landing <- readr::read_csv("../figures/source/energy/landing/plot_data.csv", 
                                 col_names = c("framerate", "fixed_kernel", "adaptable_kernel", "duration"))
```

```{r PowerLanding}
power_landing %>%
  ggplot() + 
  aes(x = framerate, 
      y = fixed_kernel, 
      size=duration) + 
  geom_point(aes(y = adaptable_kernel), color="grey") + 
  geom_point() + 
  scale_y_continuous(limits = c(3.25, 3.50)) + 
  scale_size_continuous(breaks = c(90, 120, 150)) + 
  labs(x = "Marker detection [fps]", 
       y = "Power consumption [watt]", 
       size = "Landing duration [s]") +
  theme_cowplot(font_size = 8) +
  theme(legend.position = c(1-0.025, 0.025), 
        legend.justification = c(1, 0),
        legend.box.background = element_rect(color='black', size=0.2), 
        legend.box.margin = margin(0.1, 0.1, 0.1, 0.1, 'cm')) -> p
p
ggsave('PowerLanding.pdf', p, width = 8, height=4.5, unit="cm")
```



# Plotting power consuption during object detection

```{r}
power_detection <- readr::read_csv("../figures/source/energy/tracking/plot_data_power.csv", 
                                   col_names = c("yolo", "nfold", "power")) %>%
  mutate(nfold = factor(nfold))
```

```{r PowerDetection}
power_detection %>%
  ggplot() + 
  aes(x = yolo, 
      shape = sprintf("%s fps", nfold), 
      color = sprintf("%s fps", nfold), 
      y = power) + 
  geom_point() + 
  scale_color_manual(values = c("0.5 fps" = "grey", 
                                "10 fps" = "black")) + 
  labs(x = "YOLOv3 Tiny [fps]", 
       y = "Power comsumption [watt]", 
       shape = "n-fold", 
       color = "n-fold") + 
  theme_cowplot(font_size = 8) +
  theme(legend.position = c(1-0.025, 0.025), 
        legend.justification = c(1, 0), 
        legend.box.background = element_rect(color='black', size=0.2), 
        legend.box.margin = margin(0.1, 0.1, 0.1, 0.1, 'cm')) -> p
p
ggsave('PowerDetection.pdf', p, width = 8, height=4.5, unit="cm")
```



